A data-driven study of cystic fibrosis treatment: identifying sub-types of physiotherapy style and physical activity using unsupervised clustering

### 2019-09-02 draft.tex
Fix non-rendering issue, add ACT Clustering res image.

% table 2
% table 3
% figure 4

@@

\begin{figure}
  \centering
  \caption{Sample figure caption.}
  \includegraphics[]{sample_fig}
\end{figure}

@@

\begin{table}[h]
  \caption{ACT features}
  \label{act_features}
  \centering
  \begin{tabular}{ |l|l| }
    \toprule
    \cmidrule(r){1-2}
    \textbf{Feature Name} & \textbf{Feature description} \\
    \midrule
    Breath Count & Number of breaths the person has made though an ACT  \\ 
     ~ & device during a treatment. A breath is counted if its maximum amplitude is \\ ~ & above the threshold of 8 mm H2O.\\
     \midrule
     Mean Breath Amplitude & Average breath amplitude (in mm H2O) during an ACT treatment. \\
     Minimum Breath Amplitude & Similarly minimum, maximum and standard deviation of breath amplitude. \\
     Maximum Breath Amplitude & ~ \\
     Standard Deviation of Breath Amplitude & ~\\
     \midrule
     Mean Breath Duration & Average duration (in seconds) of breath during an ACT treatment.\\ 
     Minimum Breath Duration &  Similarly minimum, maximum and standard deviation of \\ 
     Maximum Break Duration & breath duration in a treatment. \\
     Standard Deviation of Breath Duration & ~\\
     \midrule
     Break Count & Number of breaks (between breaths) in a treatment. \\
     \midrule
     Mean Break Duration & Average duration (in seconds) of breaks between breaths.\\ 
     Minimum Break Duration & Similarly minimum, maximum and standard deviation of \\ 
     Maximum Break Duration & breaks duration in a treatment. \\
     Standard Deviation of Break Duration & ~\\
     \midrule
     Set Count & Number of sets in a treatment. Prescribed treatment may have up to 10 \\
     ~ & sets. Set is a group of breaths separated by huffing and coughing activity.\\
     \midrule
     Pressure Readings Count & Number of pressure reading registered by ACT device during a treatment. \\
     ~ & Used to filter out "test" device sessions that are not part of a treatment.\\
     \midrule
     Pressures Readings Completeness Score & Data completeness score for the day \\
     ~ & If a treatment has less than 150 pressure readings it's completeness \\
     ~ & score is 0. \\
     \midrule
     Treatment Duration & Treatment duration (in minutes).\\
     \midrule
     Treatment Daily Adherence Score & Number of completed treatments out of the prescribed ones (for the \\
     ~ & given day). \\
     \midrule
     Breath Count Daily Adherence Score & Number of registered breaths across all treatments for the given day \\
     ~ & out of the prescribed amount of breaths. \\ 
     \midrule
     Treatment Rolling Weekly Adherence Score & Number of completed treatments during the last 7 days (for a given date) \\
     ~ & out of the prescribed number of treatments for this period. \\
     \midrule
     Breath Count Rolling Weekly Adherence Score & Number of registered breaths across all treatments during the last 7 days\\
     ~ & (for a given date) out of the prescribed amount of breaths for this period.\ 
     \midrule
     Treatment Weekly Adherence Score & Number of completed treatments during the last calendar week (for a given date) \\
     ~ & out of the prescribed number of treatments for this period. \\
     \midrule
     Breath Count Weekly Adherence Score & Number of registered breaths across all treatments during the last calendar week \\
     ~ & (for a given date) out of the prescribed amount of breaths for this period.\\
     \midrule
     Cumulative Adherence Score & Cumulative adherence score to date. \\
     ~ & How many in total treatments patient done over a period (since the beginning of the study out the prescribed amount.\\
     \midrule
     Breathing Time Percentage & Time in a treatment spent on an exhalation, vs not.\\
     \midrule
     Skipped Days Count & Skipped days since the last treatment. \\
     \bottomrule
    \end{tabular}
\end{table}

>>>>

% table 2
% table 3
% figure 4
Figure ~\ref{fig:act_res}  shows the four ACT clusters overlaid with a single participant (black), showing that the participant’s cluster membership changes over time. Clustering results are visualised in 2-dimensions using PCA (left) and UMAP (right). The time points are before ACT feedback (number of registered breaths) is introduced (top), after ACT feedback is introduced (middle), and once computer gaming is introduced to ACT routine (bottom). Each point represents one treatment of one participant. 
\begin{figure}[!htb]
  \centering
  \caption{ACT clusters}
  \includegraphics[]{fig_ACT_clust}
  \label{fig:act_res}
\end{figure}

@@

@@

\begin{table}[h]
  \caption{ACT features}
  \label{act_features}
  \centering
  \begin{tabular}{ |l|l| }
    \toprule
    \cmidrule(r){1-2}
    \textbf{Feature Name} & \textbf{Feature description} \\
    \midrule
    Breath Count & Number of breaths the person has made though an ACT  \\ 
     ~ & device during a treatment. A breath is counted if its maximum amplitude is \\ ~ & above the threshold of 8 mm H2O.\\
     \midrule
     Mean Breath Amplitude & Average breath amplitude (in mm H2O) during an ACT treatment. \\
     Minimum Breath Amplitude & Similarly minimum, maximum and standard deviation of breath amplitude. \\
     Maximum Breath Amplitude & ~ \\
     Standard Deviation of Breath Amplitude & ~ \\
     \midrule
     Mean Breath Duration & Average duration (in seconds) of breath during an ACT treatment. \\ 
     Minimum Breath Duration &  Similarly minimum, maximum and standard deviation of \\ 
     Maximum Break Duration & breath duration in a treatment. \\
     Standard Deviation of Breath Duration & ~ \\
     \midrule
     Break Count & Number of breaks (between breaths) in a treatment. \\
     \midrule
     Mean Break Duration & Average duration (in seconds) of breaks between breaths. \\ 
     Minimum Break Duration & Similarly minimum, maximum and standard deviation of \\ 
     Maximum Break Duration & breaks duration in a treatment. \\
     Standard Deviation of Break Duration & ~ \\
     \midrule
     Set Count & Number of sets in a treatment. Prescribed treatment may have up to 10 \\
     ~ & sets. Set is a group of breaths separated by huffing and coughing activity. \\
     \midrule
     Pressure Readings Count & Number of pressure reading registered by ACT device during a treatment. \\
     ~ & Used to filter out "test" device sessions that are not part of a treatment. \\
     \midrule
     Pressures Readings Completeness Score & Data completeness score for the day \\
     ~ & If a treatment has less than 150 pressure readings it's completeness \\
     ~ & score is 0. \\
     \midrule
     Treatment Duration & Treatment duration (in minutes). \\
     \midrule
     Treatment Daily Adherence Score & Number of completed treatments out of the prescribed ones (for the \\
     ~ & given day). \\
     \midrule
     Breath Count Daily Adherence Score & Number of registered breaths across all treatments for the given day \\
     ~ & out of the prescribed amount of breaths. \\ 
     \midrule
     Treatment Rolling Weekly Adherence Score & Number of completed treatments during the last 7 days (for a given date) \\
     ~ & out of the prescribed number of treatments for this period. \\
     \midrule
     Breath Count Rolling Weekly Adherence Score & Number of registered breaths across all treatments during the last 7 days \\
     ~ & (for a given date) out of the prescribed amount of breaths for this period. \\ 
     \midrule
     Treatment Weekly Adherence Score & Number of completed treatments during the last calendar week (for a given date) \\
     ~ & out of the prescribed number of treatments for this period. \\
     \midrule
     Breath Count Weekly Adherence Score & Number of registered breaths across all treatments during the last calendar week \\
     ~ & (for a given date) out of the prescribed amount of breaths for this period.\\
     \midrule
     Cumulative Adherence Score & Cumulative adherence score to date. \\
     ~ & How many in total treatments patient done over a period (since the beginning of the study out the prescribed amount. \\
     \midrule
     Breathing Time Percentage & Time in a treatment spent on an exhalation, vs not.\\
     \midrule
     Skipped Days Count & Skipped days since the last treatment. \\
     \bottomrule
    \end{tabular}
\end{table}
